### 2020-02-04 paper/revisions/review-responses.tex

        \question This work investigates the fuel cycle and neutronics performance of the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) with different fissile material based on an extended SERPENT-2 code. The whole paper states clearly.

        \begin{solution}
                Thank you very much for these comments. We appreciate your detailed review, which has certainly improved the paper. The manuscript has been enhanced and more detail is described regarding these changes in the specific comment responses below.
        \end{solution}

        %---------------------------------------------------------------------

        \question In the SD-TMSR burnup calculation, how are the depletion regions and burnup time step defined?
        \begin{solution}
        		  Thank you for the excellent point.

        		  About depletion regions definition: we used depletion mode 1 in Serpent-2 (i.e. burn 1), this means that the fuel material is not divided and all occurrences of it are treated as a single depletion zone. The fuel is liquid -it well- mixed all the time due to turbulent flow and mixing in the pump.

        		  About burnup time step definition: it is time interval given in days. During burnup time step the SD-TMSR should be critical and total fuel mass is almost constant (dm $\leq$ 0.1\%). We started our calculations by 30 days' time step but we do not find significant changes in K$_{eff}$ when we increased the time step to 365 days. The maximum change in K$_{eff}$ was $\leq$ 0.02\%), therefore we adopted 365-day as a time step for the following calculations.

@@

        \end{solution}

        %---------------------------------------------------------------------
        \question During the molten salt reactor operation, part of fuel salt flows outside of reactor core then the fission reaction is not happened in external loop, however the decay reactions happens everywhere. In other words, during one burnup step, the fission reactions occur in only part of the time (depends on the ratio of time taken in fuel salt passing reactor core and external loop), and nuclides' decay or other reactions occur in the whole burnup step time. Have you considered this in SERPENT calculation?  
        \begin{solution}
		          Thank you for your insightful comment. We usually use total fuel salt inventory in the primary loop to define the fuel material in the SERPENT input. Moreover, we should reduce power density accordingly because fission takes place only in the core. In our calculations, we introduce the total power instead of power density and SERPENT automatically divides total power by total fuel volume.

### 2020-02-04 cover-letter/cover-letter.tex
solve issue #34^C

		Please find enclosed a manuscript entitled: ``Various strategies for thorium fuel cycle transition in the SD-TMSR'' which I and my coauthors (Mr. Andrei Rykhlevskii, Prof. G. V. Tikhomirov, 
		and Prof. Kathryn D. Huff) are submitting for publication as a research article 
		in Annals of Nuclear Energy. The presented manuscript is 100\% original and never been published in any form (symposia, conferences, etc).

		This manuscript investigates the fuel cycle and neutronics performance of the single-fluid double-zone thorium molten salt reactor (SD-TMSR) with different fissile material loadings at startup: High Assay Low Enriched Uranium (HALEU) (19.79\%), Pu mixed with HALEU (19.79\%), reactor-grade Pu, transuranic elements (TRU), and $^{233}$U, using SERPENT-2 Monte Carlo code. This manuscript provides feasible strategies for thorium fuel cycle transition in the SD-TMSR based on reactor-grade Pu and transuranic elements (TRU) results.

		Declarations of interest: none\\

		Thank you for your consideration of our work.

		Your quick response will be highly appreciated.

>>>>

		Please consider our revised manuscript, ``Strategies for thorium fuel cycle transition in the SD-TMSR'', which I and my coauthors (Mr. Andrei Rykhlevskii, Prof. G. V. Tikhomirov, 
		and Prof. Kathryn D. Huff) are submitting for publication as a research article 
		in Annals of Nuclear Energy.

		We appreciate the interest that the editors and reviewers have taken in our manuscript and the constructive suggestions they have given. We have addressed the major concerns of the reviewers. It is our belief that the manuscript is substantially improved after making the suggested edits.

		Following this letter is the detailed response to reviewers. We included the 
	    answers in the manuscript. Changes made in the manuscript are marked using track changes.

		%Declarations of interest: none\\

		Thank you again for consideration of our revised manuscript.

### 2020-02-04 paper/methods.tex
solve issue #34^C

Simulation of liquid-fueled Molten Salt Reactor (MSR) systems requires 
computational software that can support online fuel salt reprocessing and 
refueling \cite{serp2014molten}. In this work, SERPENT-2 version 2.1.31 \cite{leppanen2014serpent} simulates the 
Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) full-core with various initial fuel types. This extension 
of SERPENT accounts for continuous online reprocessing and refueling 
\cite{aufiero2013extended}. The ENDF-VII.0 cross section library was used for all 
calculations in this work. The results demonstrate full-core runs of 
$1.25\times 10^7$ neutron histories per depletion step. The full burnup time of 
the SD-TMSR was 60 years with statistical error in $k_{eff}$ equal to $\pm$ 
$12$ $pcm$. The online extraction of \gls{FPs} and other neutron absorbers 
provides many benefits for MSRs. For example, it has the potential to reduce the initial 
fissile material inventory required to achieve criticality and improve the 
breeding ratio. Figure~\ref{fig:flow} shows a flow chart of the calculation 
steps.

>>>>

Simulation of liquid-fueled Molten Salt Reactor (MSR) systems requires 
computational software that can support online fuel salt reprocessing and 
refueling \cite{serp2014molten}. In this work, SERPENT-2 version 2.1.31 \cite{leppanen2014serpent} simulates the 
Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) full-core with various initial fuel types. This extension 
of SERPENT accounts for continuous online reprocessing and refueling 
\cite{aufiero2013extended}. The ENDF-VII.0 cross section library was used for all 
calculations in this work. The results demonstrate full-core runs of 
$1.25\times 10^7$ neutron histories per depletion step. During depletion step the SD-TMSR should be critical and total fuel mass is almost constant (dm $\leq$ 0.1\%). We started our calculations by 30 days' time step but we do not find significant changes in K$_{eff}$ when we increased the time step to 365 days. The maximum change in K$_{eff}$ was $\leq$ 0.02\%), therefore we adopted 365-day as a time step for the following calculations.
The full burnup time of 
the SD-TMSR was 60 years with statistical error in $k_{eff}$ equal to $\pm$ 
$12$ $pcm$. 
During the molten salt reactor operation, part of fuel salt flows outside of reactor core then the fission reaction is not happened in external loop, however the decay reactions happens everywhere. We use total fuel salt inventory in the primary loop to define the fuel material in the SERPENT input. Moreover, we should reduce power density accordingly because fission takes place only in the core. In our calculations, we introduce the total power instead of power density and SERPENT automatically divides total power by total fuel volume.

The online extraction of \gls{FPs} and other neutron absorbers 
provides many benefits for MSRs. For example, it has the potential to reduce the initial 
fissile material inventory required to achieve criticality and improve the 
breeding ratio. Figure~\ref{fig:flow} shows a flow chart of the calculation 
steps.
